\documentclass[10pt]{article}

\usepackage{hyperref}
\usepackage[utf8]{inputenc}


\title{Artifical Intelligence}
\author{
        Henry Huck \\
        Master Specialisé - HEC \\
        \and
        Romain Lapeyre\\
        Grande Ecole - HEC\\
}
\date{\today}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\maketitle
\thispagestyle{empty}
\pagenumbering{gobble}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Quote Page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\phantom{TEXT}
\thispagestyle{empty}
\pagenumbering{arabic}

\vspace{200pt}
\begin{quotation}
\noindent \textbf{Human:}  \textit{\lq What is the purpose of emotions ?\rq }\\
\textbf{Machine:} \textit{\lq I don't know.\rq}
\end{quotation}

\vspace{270pt}

\begin{flushright}
   From Google's research paper \lq A Neural Conversation Model\rq. \cite{seq2seq}
\end{flushright}


\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Table of contents %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Acknowldgements %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Acknowledgments

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Intro %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Introduction}\label{introduction}

%Introduction about super intelligence and the theories relative to it
Super intelligence and singularity \cite{Kurzweil}

Computer Equivalent to Human , super intelligence, strong AI \cite{Turing}


Strong AI is (maybe) not possible \cite{ChineseRoom}

IBM's victory at Jeopardy, called \lq An ingenous program, not a computer that
can think\rq

\footnote{
\href{http://cacm.acm.org/magazines/2012/1/144824-artificial-intelligence-past-and-future/fulltext}
{Artificial Intelligence: Past and Future}}

%Back to reality and what is currently possible

Whatever, a computer beat a human in a question / answer game

AI has developed, cite several sucess. Car. video game atari. Siri.
%

The purpose of this paper is to give a general overview of the recent
improvements in Artifical Intelligence studies. It is not intended to be a
highly technical paper, but rather an overview of the state of the art
techniques in Artifical Intelligence and Machine Learning.

\noindent Firstly, we will present a brief history of Artifical
Intelligence studies, along with the latest models used in Natural Language
Processing and their applications.

\noindent Then, we'll examine the implications of Artificial Intelligence
progress for the Entrepeurial Ecosystem. In particular, we'll see the impact on
specific industries such as the car industry, and the impact it will have on
interfaces.

\noindent Lastly, we'll see what are today's limitations, and what remains to be
achieved before all these breakthroughs start being really usable.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% First part %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Recent improvements in ML technologies}

\subsection{A bit of History}


\subsection{Why is AI progressing faster and faster?}

\subsubsection{Cheap parallel computation}

\subsubsection{Progress in Models}

\subsubsection{Access to big datasets}

Models are better when trained on bigger datasets

\subsection{Modern Models and their applications}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Second Part %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{The impact of AI on the entrepreneurial ecosystem}

Now that we've seen the improvements of AI technology, we're going to look at
the impact those technologies can have on the entrepreneurial ecosystem.
Our approach will be the following: we'll explore a few applications of AI
technologies, and propose startup ideas related to this.

Of course, some companies, including startups, are already leveraging the latest
 progress in AI to offer a commercial service, or are expected to do so.
 We'll therefore start by reviewing the first AI commercial progress in the
 space. Then, we'll look at other area to expend our analysis

\subsection{Impact on startup ideas}

\subsubsection{Self-driving cars}

\paragraph{A bit of context}

The first autonomous cars appeared back in the 1980's with the Canergie Mellon
Unviversity Navlab project in 1984, and a similar project by Mercedes Benz in
1987. Those project were were considered pure exploration at the time.
But things have changed. In 2005, DARPA launch a Grand Challenge which was won
by a team of engineers at Stanford, who created a first self-driving car
prototype. Since then, the team has been hired by Google to create the first
autonomous that has started hitting the road of California in the spring 2015.
A few others are following this way: Uber, Tesla and potentially Apple to name
a few.

\subsubsection{Technology behind those cars}

Let's look at the technology behind those.
\\
First, autonomous car include a ton of sensors to gather data about their
environment. Let's look into those.
\\
The position of the car is determined with a classic GPS, to which are added
tachometers, altimeters and gyroscopes to enrich the only GPS data. Then come
radar sensors that are located all around the car to localize potential
obstacles. Usually, there are 4 of those: 3 at the front and 1 at the back of
the car. On the sides of the car, there are ultra sonic sensors which are a bit
different, they're used to locate objects close to the car. Think about parking
for instance.

\noindent On top of this, a video camera points to the front. It aims to detect
traffic lights and road signs. The central element among all those sensors is
the LIDAR: Light detection and ranging. This element is located at the top of
the car. It identifies the edges of the road, and provides a 360 projection of
the environment around the car.

\url{http://students.cec.wustl.edu/~daniel.gordon/Tech_Writing/GoogleCarDiagram.jpg}

Second, the car includes a powerful computer to analyze all these parameters
and actually \lq drive\rq the car. Let's take the example of Google's software
called \lq Chauffeur \rq . It's composed of two parts. One is hardcoded
(road signs, traffic lights colors), and one is a learning part. Every mile is
logged and provides additionnal data on how the car should drive itself.
Therefor, the car is able to predict the behavior of surrounding elements
(both car, bikes, pedestrians). Such things are based on neural networks behing
fed with the driving data of million of other cars
that Google has been collecting. This video by Google provides a great example
of how the car perceives its environment and can make decisions.

\url{http://i.telegraph.co.uk/multimedia/archive/03183/google1_3183549c.jpg}

\url{https://www.youtube.com/watch?v=dk3oc1Hr62g}


\subsubsection{Car industry discruption}

The disruption is happening at several levels: some startups are building addons
to current cars, so they can get self-driving functionnalities. For instance,
a Californiancompany called Cruise
\footnote{\href{http://www.getcruise.com}{Cruise Website}}
enhances a car's capabilities by seamlessly integrating self-driving car
capabilities to your existing car. It works by adding sensors and a computer to
the car, and works in a similar fashion as the Google car. The idea is that you
can add those features to your car for about \$ 15,000 depending on the vehicle
you have. Google has a similar approach: according to several journalistic
sources, they intend to resell their self-driving technologies to automotive
companies. Though, many people fear that Google will have a significant
bargaining advantage, as those car companies don't have the technology yet.

Some other companies intend to replace current car makers. Tesla is the best
example in the category. Though the company CEO, Elon Musk, is confident
self-driving cars will hit the market by 2020, there were no public statement
about Tesla building such cars. In a recent video, he was asked whether Tesla
would be willing to provide Uber with self-driving cars, and declined to answer.
Many reporters concluded that Tesla will likely be the first company to sell
autonomous cars, that were built in-house. Similar to Tesla, there could be new
car giants rising by leverging the opportunity to build both a new type of car
and a powerful self-driving technology.

Finally, the most ambitious model is probably the one by Uber. The idea behind
it is that using UberX costs about \$ 2.15 per mile (source: AKA research).
Owning a personal car is \$ 0.76. Uber wants to create Car-As-a-Service.
The idea is similar to what Uber is today, but without the drivers. Think about
it for a moment. The car driver accounts for most of the cost of an UberX ride.
Therefore, if you can remove the driver, the cost would be \$ 0.25 per mile.
It's not only about replacing the driver, it's about making the car available
for customers at any time, on any day. Whereas a driver takes some rest and
parks their car, a self-driving car could be on the road almost 24/7.
\\
\url{http://static3.businessinsider.com/image/55dfd176bd86ef19008b67fe-700-465/vehicle-cost.png}
\\
No matter who's leading that change, it's likely that our own definition of the
car is going to change. Mercedes has shown an example of a car being similar to
a living room: the Mercedes-Benz F 015. Travellers could sleep, chat, browse the
internet as if they were at home. The car has been driving around San Francisco
this year.
\\
\url{https://www.mercedes-benz.com/wp-content/uploads/sites/3/2015/01/05-Mercedes-Benz-F-015-Luxury-in-Motion-680x436.jpg}
\\

Another big change would be the oil station network. Since the car could drive
themselves to refill, or could be fully electricity powered, it will most likely
be the end of oil stations as we know them. Those will be probably automated as
well, and moved to non-residential areas.


\subsection{Speech \& natural-language recognition, or the death of interfaces}

The speech recognition movement has been initiated to the large public with a
startup bought by Apple, Siri. This startup was initiated a DARPA project as
well named CALO. Essentially, it works by transcripting speech to text, and then
parses the text to perform actions. Google has launched a similar service called
Google now. Both these system can perform actions based on the user's speech.
This technology enables the user to perform actions on the service of his
choosing (OpenTable, Yelp), without having to use any interface. The speech is
the communication tool.

\subsubsection{Technology behind it }
Personal assistant technologies rely on three parts.
The first one is about extracting the meaning of the speech to figure out which
action to perform. In that case, Siri uses for instance part of speech tagging,
noun-phrase chunking, dependency \& constituent parsing. On the other side,
such service should plug into third party services. The complexity lies in the
ability to connect with very various systems (AirBnb, HotelTonight, Couchsurfing
,Bookking.com only to make a hotel reservation). Once this has been done, Siri
needs to communicate back with the user, converting API responses to oral \&
human communication.

\subsubsection{Use cases}
Plenty of services have followed the Siri path, usually in a more advanced
fashion. It's interesting to note that some services are built with technology
at its core (Siri \& Google Now), whereas others are human-based at first. The Y
Combinator startup called \lq Magic\rq  is the exact opposite. The service only
includes the written language recognition. For instance, a user can text Magic
asking for anything they'd like, and then the service will connect to thirt
party services (in a similar fashion than Siri) to provide the service live. The
complexity therefore lies on relying on a very large number of 3rd party
services to provide a very large offering to the user. When a regular supermarket
has a limited inventory, Magic, as a personal assistant, needs to be able to
deliver anything the user wants. The second part of the complexity is scaling.
When you have human handling each operation at the beginning, you need to
progressively create processes to better handle certain tasks, and eventually
automate entire parts of the workflow.

Combining AI and diversity of requests doesn't seem to be possible today. Such
startups are having trouble to scale. The current solution is to combine a mix
of the two. Facebook Messenger recently launched a service called M that
illustrates it: they've leveraged the purchase of the French startup Wit.ai and
a team of personal assistants that handle manually some request to provide this
personal assistant service.

This market is likely a winner takes all one. Since these personal assistant
platforms are about connecting people with services, their model is similar to
Google's search engine. If you are the entry point for the customer, it's very
hard for competitors to make the users switch. Startups like Magic benefited
from their speed of execution, but the ability to scale requires to leverage AI
technology. It's not clear today whether startups or giants will succeed in that
field. Though it's interesting to see that the 2 take 2 opposite approach to
later converge in the same area.

Additional services from startup in that space intend to focus on one vertical
only. A good example of it are personal assistant focused on organizing meetings
between to person who want to schedule an appointment. To name a few, players in
that space are x.ai, assistant.ai or juliedesk. These companies are managing to
live up to their promise, but the complexity once again lies in the ability to
scale. They are strongly investing in AI to replace human services that they
first relied on.

Finally, we could imagine two models for that space.
One would be a model built by a major tech company (among Facebook, Google or
Apple) that would provide any kind of service by levering a strong AI
technology, and would plug into a very large number of APIs from company that
provide food delivery, order delivery, or pretty much anything.
The second model would be a platform one. A company like Magic could be the
entry point for the user. Then, if a calendar request is made to Magic, it would
just have to tag it as so and to route it to a Calendar booking service such as
x.ai.

The former seems more likely as concentrating the efforts in Machine Learning is
probably the best approach to achieve the best results, though the two are
possible.

\subsubsection{Death of interfaces}

The main benefit of such services for the user is that it's a very easy way to
communicate with a machine, in order to get a service. Think about the
User-Experience behind it. If you use a speech recognition, you would just
have to say: \lq Book me a table for 2 in a historic area of Paris, where I
can eat italian
food.\rq. That will do the trick.
If the user was to do it on their laptop or on their phone, they'll need to:
\begin{itemize}
  \item Find the right service to search on (TripAdivisor, OpenTable, Yelp?).
  \item Perform the search.
  \item Make a choice
  \item Go through the reservation process.
\end{itemize}

The former is way faster. Another benefit is in what we would call \lq unique\rq
cases. Say you want to book a laser-tag party in Paris, and you've never done it
before. You don't know where to look, so you're going to spend time figuring out
how to book a good laser-tag game. You'll probably need to benchmark a few,
look at the review, etc.

A strong case in favor of speech-based application is that you don't need to
learn about the existence of the service, and you don't need to use any
interface. UX designers often struggle to make an app available to all. No
interface is probably the most efficient. Even a 80 year-old who has never used
an app in their life would be able to use it. We can then imagine that, instead
of having dozens of apps on our phone or dozens of websites pinned on our
browsers, a single personal assistant app could do the job. Just like Google
does for search today. This user experience part make those personal assistant
particularly appealing in the long-run, because the friction to start using them
is very low. A good example of it we saw is about forwarding professional
expenses to the company's accountant. The mainstream service for it today is
Expensify. You just need to install an app on your phone (meaning, if you have
1000 people in the company, they all need to install it), then you can take a
picture of a receipt and it will automatically be sent to the company's
accoutant. This all process would be easier with a speech or written language
recognition app. You could just send over the receipt's picture via text to the
company AI bot. It will recognize what it is, potentially ask a few question
about the expense and done.

Time will tell, but usually the service that provides the simplest user
experience wins. And it's likely that the personal assistant user experience is
the simplest.


\subsubsection{Image recognition}

\subsection{Impact on startup structures}

\subsubsection{New kinds of business models}

\paragraph{The path to the 100 per cent software company}


\pagebreak
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 3rd Part %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Limits}




Sources

\section{Car}

\url{http://www.google.com/selfdrivingcar/}
\url{http://www.businessinsider.com/why-uber-is-investing-in-autonomous-cars-2015-8?IR=T}
\url{http://www.entrepreneur.com/article/243751}
\url{http://www.forbes.com/sites/chunkamui/2014/08/04/5-reasons-why-automakers-should-fear-googles-driverless-car/}
\url{http://my.teslamotors.com/fr_CH/forum/forums/tesla%E2%80%99s-musk-sees-fully-autonomous-car-ready-5-years}

\section{Speech recognition}


\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Conclusion %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}\label{conclusion}

\pagebreak


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Bibliography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{thebibliography}{40}

  \bibitem{seq2seq} Oriol Vinyal \& Quoc V. Le,
  {\em A Neural Conversation Model}, Google - June 2015

  \bibitem{Kurzweil} Ray Kurzweil, {\em The Singularity is near} - 2005

  \bibitem{Turing} Alan Turing, {\em The Imitation Game} - 1950

  \bibitem{ChineseRoom} John Searle, {\em Minds, Brains, and Programs},
  Behavioral and Brain Sciences - 1980

  \bibitem{RusselAI} Stuart Russel \& Peter Norvig

  {\em Artificial Intelligence - A Modern Approach, 3rd Edition} - 2010.



\end{thebibliography}


\end{document}
